Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
remove section
no low rank hypothesis

Finally since there is a high correlation between neurons, we made a
low-rank hypothesis and perform noise filtering through a principal component
analysis. From the $p$ eigen vectors, we kept $80\%$ of
the eigen vectors which have the largest eigen value. In the context of the
challenge, this assumption was deduced from ground truth of provided network.

@@

% TODO
%   - discussions about the results
%   - discussions about the metrics (Gilles text)

@@

\subsection{Discussion about the metric}
\label{sec:metric}

>>>>

Finally since there is a high correlation between neurons, we perform noise
filtering through a principal component analysis. From the $p$ eigen vectors,
we kept $80\%$ of the eigen vectors which have the largest eigen value. In the
context of the challenge, this assumption was deduced from ground truth of
provided networks.

@@

% TODO
%   - discussions about the results
%   - discussions about the metrics (Gilles' text)

@@
